DINO Methods for Style Transfer

### 2022-04-19 paper/Paper.tex
bug fix
typos

\begin{center}
\includegraphics[width=14cm]{comparison}	
\caption{Style transfer results across different experiments.}
\label{comparison}
\end{center}

\begin{figure}
	\includegraphics[scale=0.35]{comparison}

\end{figure}

In both experiments A and B, we can see that as training progresses, the model gradually learns to render the content image to the style of the style image. But in both cases, certain details of the objects depicted in the content image are lost. Experiment A seems to have less feature losses while experiment B produces style-transferred images that are closer to what the original style transferer produces (columns A, B, Original, figure \ref{comparison}). For experiment A, we can see both the content and style losses decrease over time. Meanwhile, experiment B has a decreasing style loss but its content loss first decreases and then increases before oscilating more.

@@

During its training process, experiment D seems to be slowly learning to replicate the content image while not paying much attention to the style image. The resulting outputs started as poor-quality content images, but they slowly converged to the content images with some slight color variations (column D, figure \ref{comparison}). We see the content loss slowly decreases as training progresses while the style loss oscilates and shows no signs of improvement.

>>>>

\begin{center}
\begin{figure}
\includegraphics[width=14cm]{comparison}	
\caption{Style transfer results across different experiments.}
\label{comparison}
\end{figure}
\end{center}

In both experiments A and B, we can see that as training progresses, the model gradually learns to render the content image to the style of the style image. But in both cases, certain details of the objects depicted in the content image are lost. Experiment A seems to have less feature losses while experiment B produces style-transferred images that are closer to what the original style transferer produces (columns A, B, Original, figure \ref{comparison}). For experiment A, we can see both the content and style losses decrease over time. Meanwhile, experiment B has a decreasing style loss but its content loss first decreases and then increases before oscillating more.

@@

During its training process, experiment D seems to be slowly learning to replicate the content image while not paying much attention to the style image. The resulting outputs started as poor-quality content images, but they slowly converged to the content images with some slight color variations (column D, figure \ref{comparison}). We see the content loss slowly decreases as training progresses while the style loss oscillates and shows no signs of improvement.
